### 2019-01-13 papers/journal/related.tex
Addded references to the related work

\todo{Add references}
The Boolean satisfiabilty (SAT) solvers are used to solve wide range of problems including
%
software and hardware verification, equivalence checking, automatic test generation,
AI planning, scheduling and program synthesis. 
%
The enormous progress in the performance of SAT and SMT solvers
%Improvement in SAT and SMT solvers
in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 
%
Many of which involve reasoning about graphs and networks rules~\cite{guerra2012reasoning,chin2008biographe} with possible exhaustive search.
% and hence can be reduced to solving a SAT/SMT question. 
%

>>>>

The Boolean satisfiabilty (SAT) solvers are used to solve wide range of problems including
%
software and hardware verification~\cite{biere1999symbolic1, biere1999symbolic2, bjesse2001finding, velev2003effective}, equivalence checking~\cite{goldberg2001using} automatic test case generation~\cite{stephan1996combinational},
AI planning~\cite{kautz1996pushing} and scheduling~\cite{gomes1998randomization}. 
%
The enormous progress in the performance of SAT and SMT solvers
%Improvement in SAT and SMT solvers
in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 
%
Many of which involve reasoning about graphs and networks rules~\cite{guerra2012reasoning,chin2008biographe} with possible exhaustive search.
% and hence can be reduced to solving a SAT/SMT question. 
%
